We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-21 paper/paper.tex
references

To date, the atipicallity of satellite distributions can only be
addressed in simulations.
First studies 
Most of the studies have been performed in the currently preferred
paradigm, which is based on a Cold Dark Matter cosmology in a expanding
Universe described by General Relativity including a Cosmological
Constant, the so-called Lambda Cold Dark Matter (LCDM) model.
The broad consensus is that these highly structured satellite distributions
are hard to find in simulations \citep{}.  
There are still disagreements on the precise degree of atypicallity
and the conditions required to simulate satellite distributions closer.
These disagreements seem to be originated on what is considered to be
a LG analog in the simulation.

>>>>

To date, the atipicallity of satellite distributions can only be
addressed in simulations.
First studies 
Most of the studies have been performed in the currently preferred
paradigm, which is based on a Cold Dark Matter cosmology in a expanding
Universe described by General Relativity including a Cosmological
Constant, the so-called Lambda Cold Dark Matter (LCDM) model.
The broad consensus is that these highly structured satellite distributions
are hard to find in simulations. 
There are still disagreements on the precise degree of atypicallity. 
\cite{2015MNRAS.452.3838C} showed that part of the disagreement is the
ambiguitiy in defining a planar configuration, finding that actually
planar structures show a large diversity, hindering the possibility to
use one or to systems as a cosmological probe.
